Deterministic Scheduling of Periodic Messages by an SDN Approach

### 2017-07-21 infocom/infocom.tex
figures reduites

       \begin{center}
	 \scalebox{0.8}{
\begin{tikzpicture}

@@

      The following experimental results compare the three presented algorithms.
      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution, depending on $P$, $\tau$, $n$ and the size of the routes. On the other hand, the exhaustive search finds an optimal solution if it exists, but works in exponential time. We compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
      From our C-RAN context we choose the following parameters: the number of routes 
      is at most $n = 20$, $\tau$ is equal to $2500$. Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.

@@

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.53\textwidth]{periode_petite.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Minimum period averaged over $1000$ random instances}
      \end{figure}

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.5\textwidth]{echec_longues.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate for $8$ routes over $1000$ random instances}
     \end{figure}

@@

%     \begin{algorithm}[H]
%     \caption{ Minimized Scheduling Periodic (MSP)}
%     \begin{algorithmic}
%     \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
%     \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists
%   
%     \FORALL{route $r_{t_i}$}
%     \STATE  $w_i \leftarrow 0$
%     \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
%     \FORALL{route $r_{t_j}$}
%     \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
%     \STATE $deadline \leftarrow$ min(deadline-route,period-end)
%     \ENDFOR
%     
%     \STATE Call (MS)
% 
%     
%     \ENDFOR
% 
%     \STATE return the best $(P,\tau)$-periodic assignment, or FAILURE
% 
%     \end{algorithmic}
%     \end{algorithm}

    \subsection{Experimental evaluation}
    \label{sec:resultsPALL}

    In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
    We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
    We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
    For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
    Hence, for a routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks 
    whith different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
    In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed. In our experiments the margin range from  $0$ to $3000$ slots.
   We look at two different regimes: we take a period equal to $1,05n\tau$ to represent a very loaded network
   and $1,5n\tau$ for a mildly loaded network. Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}. We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star routed networks. Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.

  \centering
     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
\vspace{-0.75cm}
      \caption{Success rate of different orders, $95\%$ load.}
          \end{figure}
          \vspace{-1cm}
\begin{figure}[H] 
          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
          \vspace{-1.5cm}
      \caption{Success rate of different orders, $80\%$ load.}
           \label{fig:success30000}
     \end{figure}

@@

    \begin{figure} [H] 
       \begin{center}
      \includegraphics[width=0.5\textwidth]{retour_21000.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
     \label{fig:success21000}
     \end{figure}

@@

       \begin{center}
     \hspace{-0.5cm} \includegraphics[width = 0.5\textwidth]{stochastic.pdf}
       %\input{figures/stochastic}
      \end{center}
      \vspace{-1cm}
      \caption{Needed margin with respect to the period for a stochastic policy}
      \label{fig:sto}
     \end{figure}

>>>>

       \begin{center}
	 \scalebox{0.6}{
\begin{tikzpicture}

@@

      The following experimental results compare the three presented algorithms.
      Notice that both Greedy algorithm and Shortest-Longest are polynomial time algorithm but are not always able to find a solution, depending on $P$, $\tau$, $n$ and the size of the routes. On the other hand, the exhaustive search finds an optimal solution if it exists, but works in exponential time. We compare the performance of the algorithms in two different regimes: routes are either short with regard to $\tau$, or unrestricted.
      From our C-RAN context we choose the following parameters: the number of routes 
      is at most $n = 20$, $\tau$ is equal to $2500$. Moreover the period is always larger than $n\tau$ otherwise no assignment is possible and smaller than $3n\tau$ otherwise the greedy algorithm always returns a solution.

@@

      \begin{center}
	 \hspace{-0.5cm}\includegraphics[width=0.315\textwidth]{periode_petite.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Minimum period averaged over $1000$ random instances}
      \end{figure}

@@

       \begin{center}
      \hspace{-0.5cm}\includegraphics[width=0.3\textwidth]{echec_longues.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate for $8$ routes over $1000$ random instances}
     \end{figure}

@@

%     \begin{algorithm}[H]
%     \caption{ Minimized Scheduling Periodic (MSP)}
%     \begin{algorithmic}
%     \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
%     \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, if it exists
%   
%     \FORALL{route $r_{t_i}$}
%     \STATE  $w_i \leftarrow 0$
%     \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
%     \FORALL{route $r_{t_j}$}
%     \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
%     \STATE $deadline \leftarrow$ min(deadline-route,period-end)
%     \ENDFOR
%     
%     \STATE Call (MS)
% 
%     
%     \ENDFOR
% 
%     \STATE return the best $(P,\tau)$-periodic assignment, or FAILURE
% 
%     \end{algorithmic}
%     \end{algorithm}
    \subsection{Experimental evaluation}
    \label{sec:resultsPALL}
    In this section, we first try to understand what is the best choice of order for the first stage of the algorithm.
    We fix the number of routes to $8$ to make comparisons with the results of Section~\ref{sec:exp_PAZL} easier. 
    We draw uniformly the weights of the arcs between $0$ and $20000$ slots.
    For a given routed network, we define the {\em margin} as the difference between $T_{max}$ and twice the longest route. 
    Hence, for a routed network choosing the margin or $T_{max}$ is the same, but since we will consider many networks 
    whith different longest route's size, it will be more meaningful to set the margin rather than $T_{max}$.
    In fact the margin represents the latency imposed by the communication process without taking into account the physical length of the network which cannot be changed. In our experiments the margin range from  $0$ to $3000$ slots.
   We look at two different regimes: we take a period equal to $1,05n\tau$ to represent a very loaded network
   and $1,5n\tau$ for a mildly loaded network. Choosing a larger period is not relevant since then we know how to solve the problem even without waiting times as shown in Section~\ref{sec:exp_PAZL}. We represent the success rate with regards to the margin, for the five kind of orders using the Greedy algorithm for the second stage, computed over $10000$ random star routed networks. Note that for the random order, we compute $1000$ random orders and count it as a success as soon as there is a solution for one order.

\begin{figure}[] 
    \begin{minipage}[c]{0.2\textwidth}
  \centering
      \includegraphics[width=3.5cm]{departs_gp_21000.pdf}
      \caption{Success rate of different orders, $95\%$ load.}
      \end{minipage} \hfill
        \begin{minipage}[c]{0.2\textwidth}
          \includegraphics[width=3.5cm]{departs_gp_25000.pdf}
      \caption{Success rate of different orders, $80\%$ load.}
            \end{minipage} \hfill
                  \label{fig:success30000}
     \end{figure}
%
% 
%\begin{figure}[H] 
%  
%  \centering
%     \hspace{-1.5cm} \includegraphics[width=0.4\textwidth]{departs_gp_21000.pdf}
%\vspace{-0.75cm}
%      \caption{Success rate of different orders, $95\%$ load.}
%          \end{figure}
%          \vspace{-1cm}
%\begin{figure}[H] 
%          \includegraphics[width=0.5\textwidth]{departs_gp_25000.pdf}
%          \vspace{-1.5cm}
%      \caption{Success rate of different orders, $80\%$ load.}
%           \label{fig:success30000}
%     \end{figure}

@@

    \begin{figure} [H] 
       \begin{center}
      \includegraphics[width=0.3\textwidth]{retour_21000.pdf}
      \end{center}
            \vspace{-1cm}
      \caption{Success rate of GD, MLS and PMLS for $P = 21000$}
     \label{fig:success21000}
     \end{figure}

@@

       \begin{center}
     \hspace{-0.5cm} \includegraphics[width = 0.3\textwidth]{stochastic.pdf}
       %\input{figures/stochastic}
      \end{center}
      \vspace{-1cm}
      \caption{Needed margin with respect to the period for a stochastic policy}
      \label{fig:sto}
     \end{figure}
